\Large Carryover effects in free recall reveal how past experiences influence memories of future experiences

### 2023-01-17 paper/main.tex
finished complete draft of discussion section

@@

>>>>

Every participant in our study encountered exactly the same words, split into
exactly the same lists. But participants' memory performance, the orders in
which they recalled the words, and the effects of early list manipulations on
later lists, varied according to how we presented the to-be-remembered words.

Our findings raise a number of exciting questions. For example, how far might
these manipulations be extended? In other words, might there be more
sophisticated or clever feature or order manipulations that one might implement
to have stronger impacts on memory? Are there limits to how much impact (on
memory performance and/or organization) these sorts of manipulations can have?
Are those limits universal across people, or are there individual differences
(based on prior experiences, natural strategies, neuroanatomy, etc.) that
impose person-specific limits on the potential impact of presentation-level
manipulations on memory?

Our findings indicate that the way word lists are presented affects how people
remember them. To the extent that word list memory reflects memory processes
that are relevant to real-world experiences, one could imagine potential
real-world applications of our findings. For example, we found that
participants remembered more words when the presentation order agreed with
their memory fingerprints. If analogous fingerprints could be estimated for
classroom content, perhaps they could be utilized manually by teachers, or even
by automated content presentation systems, to optimize how and what students
remember.

@@

Our work raises deep questiong about the fundamental nature of human learning.
What are the limits of our memory systems? How much does what we remember (and
how we remember) depend on how we learn or experience the to-be-remembered
content? We know that our expectations, strategies, situation models learned
through prior experiences, and more, collectively shape how our experiences are
remembered. But those aspects of our memory are not fixed: when we are exposed
to the same experience in a new way, it can change how we remember
that experience, and also how we remember, process, or perceive
\textit{future} experiences.
